---
title: "Global Cheese Analysis: Fat Content and Characteristics"
author: "Shu Wang"
date: "2024-09-29"
format:
  html:
    toc: true
    toc-depth: 2
---

## Executive Summary

This blog explores data sourced from Cheese.com to analyze how fat content, texture, flavor, and aroma vary among cheeses from different countries. The analysis reveals that European cheeses, such as those from France, Germany, and the United Kingdom, tend to have higher fat content, contributing to their rich textures and aromas. These insights provide useful information for cheese producers aiming to optimize their products based on consumer preferences in various markets.

## Problem Description

Cheese is a globally popular food, known for its diversity in flavor, texture, and nutritional composition. This analysis focuses on how the fat content of cheese varies by country, and how this affects characteristics like texture and flavor. Understanding these patterns can help cheese producers tailor their products to consumer tastes in different regions.

## Data Description

We utilized data from Cheese.com, which includes information on the fat content, texture, flavor, and aroma of cheeses from various countries. The dataset consists of several variables that describe cheese properties such as fat content, country of origin, and type of milk used.

```{r data-loading, echo=TRUE}
# Load the cheese data from GitHub
cheeses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')

# Display the first few rows of the dataset
head(cheeses)
```

## Data Cleaning and Preparation

The data contains some missing values and non-numeric fat content entries. We clean the dataset by filtering out cheeses with missing fat content and converting the fat content to numeric values where applicable.

```{r data-cleaning, echo=TRUE}
# Load necessary libraries
library(tidyverse)
library(stringr)

# Clean the cheese data
cheese_data_clean <- cheeses %>%
  filter(!is.na(fat_content)) %>%
  mutate(
    fat_content = as.numeric(str_extract(fat_content, "\\d+")),
    country = ifelse(is.na(country), "Unknown", country)
  )

# Display cleaned data
head(cheese_data_clean)
```

